Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
summary measures of seed dispersal with dplyr
calculate all seed summary stats with dplyr

@@

df %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data = df %>% drop_na(s.id), aes(x = xloc, y = yloc)) +
  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds

>>>>

df %>% 
  drop_na(s.id) %>% 
  mutate(xi = (mean(xloc)-xloc)^2,
         yi = (mean(yloc)-yloc)^2) %>% 
  summarise(x = mean(xloc),
            y = mean(yloc),
            av.disp = mean(disp),
            se.disp = sd(disp)/sqrt(n()),
            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df

@@

df %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = s.df,
             aes(x = x, y = y), color = "Red") # Mean location of seeds
